Differentiation By Year

### 2017-11-18 doc/RMD/by-year.Rmd
update Figure 6 to PeerJ's standards

```{r dapc_plot_newamica, fig.width = 5, fig.height = 4, warning = FALSE, message = FALSE}
gg_region_year_micanewa <- ggscatter(regyear.dapc, strata(dat11cc), filter = quo(Region %in% c("WA", "CA", "NE", "MI"))) +
  facet_wrap(~Region, nrow = 2) +
  theme(legend.position = "right") +
  theme(legend.justification = "bottom") +
  scale_color_manual(values = yearscale, breaks = names(yearscale)) +
  theme(legend.box.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(legend.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank()) +
  theme(legend.key = element_rect(fill = "grey95"))
gg_region_year_micanewa
if (!interactive()) {
    ggsave(filename = file.path(PROJHOME, "results/figures/publication/dapc_region_year_micanewa.pdf"),
       plot = gg_region_year_micanewa,
       width = 88,
       height = 0.8*88,
       units = "mm",
       scale = 1.25
       )
}
```

>>>>

```{r dapc_plot_newamica, fig.width = 5, fig.height = 4, warning = FALSE, message = FALSE}
gg_region_year_micanewa <- ggscatter(regyear.dapc, strata(dat11cc), filter = quo(Region %in% c("WA", "CA", "NE", "MI"))) +
  facet_wrap(~Region, nrow = 2) +
  theme(legend.position = "right") +
  theme(legend.justification = "bottom") +
  scale_color_manual(values = yearscale, breaks = names(yearscale)) +
  theme(legend.box.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(legend.margin = unit(c(0, 0, 0, 0), "lines")) +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank()) +
  theme(legend.key = element_rect(fill = "grey95"))
# 2017-11-18
# PeerJ has asked for me to label this figure with A-D for silly reasons
gg_region_year_mincanewa_lab <- gg_region_year_micanewa %+%
  mutate(gg_region_year_micanewa$data, 
         Region = case_when(
           Region == "NE" ~ "A (NE)",
           Region == "MI" ~ "B (MI)",
           Region == "WA" ~ "C (WA)",
           Region == "CA" ~ "D (CA)"
         ))
gg_region_year_mincanewa_lab
if (!interactive()) {
    ggsave(filename = file.path(PROJHOME, "results/figures/publication/dapc_region_year_micanewa.pdf"),
       plot = gg_region_year_mincanewa_lab,
       width = 88,
       height = 0.8*88,
       units = "mm",
       scale = 1.25
       )
}
```
